---
title: "Assignment3"
author: "Ohad Dali"
date: "December 25, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("igraph")
```

#Assignment 3 - Task 1 
##Network Analysis

###Grey Anatomy network of romance - Centrality


Let's load the Grey Anatomy network of romance and plot the graph
```{r}
library(igraph)
ga.data <- read.csv('ga_edgelist.csv', header = TRUE , stringsAsFactors = FALSE)
g <- graph.data.frame(ga.data,directed = F)
plot(g)
```

Now let's focus on the big component of the graph.

```{r}
g_ <- delete.vertices(g, c('adele','chief','susan grey','thatch grey','ellis grey','tucker','bailey','ben'))
plot(g_)


```
####i. By Betweeneess
We calcualte the betweeneess of each node in the new graph, and get the node with the highest betweeneess.
```{r}
bet<-betweenness(g_)
bet[v==max(bet)]
```

Like we can see , Sloan is the actor with the highest betweeneess(115.3667)

####ii. By Closeness

In the same way as before, we calculates the closeness of each node and get the maximum.

```{r}
clo <- closeness(g_)
clo[which.max(clo)]
```

We can see that Torres has closeness of 0.01754386, which it the highest in the graph.

####iii. By Eigenvector


```{r}
eig <- eigen_centrality(g_)
eig$vector[which.max(eig$vector)]
```
Karev is the actor with the highest value of eigenvector.
